\section{Conclusion, Development Context, and Reflection}
\label{sec:conclusion}

This study reproduced the core idea of GuP through a correctness-oriented implementation for exact subgraph matching. It includes a literature taxonomy, a clear reproduction-scope statement, experiments on three successful datasets, a filtering-strategy ablation study, and a small extension on result reuse for related queries.

From the perspective of the development history of subgraph matching, the field has evolved from earlier candidate-space and access-method ideas~\cite{he2008graphql} toward increasingly integrated systems that combine filtering, order optimization, conflict reuse, and execution engineering~\cite{han2019daf,sun2020study,sun2021rapidmatch}. GuP is an instructive modern point in this development line because it emphasizes dynamic, state-aware pruning while remaining conceptually decomposable into interpretable modules.

Our results lead to four main conclusions. First, the experiments on \texttt{Yeast}, \texttt{Human}, and \texttt{HPRD} cover both lighter and heavier search regimes. Second, reservation-based pruning is the only reproduced GuP mechanism that contributes clear and repeated search-space reductions on the current workloads. Third, the current Python prototype still has a visible scalability boundary, as shown by the boundary runs on \texttt{WordNet} and \texttt{Patents}. Fourth, under a restricted related-query setting, previously materialized result mappings can be reused exactly and can substantially reduce the incremental cost of query refinement, as shown by the optional Human query-pair experiment.

One clear lesson from the study is that paper reproduction involves more than matching a final table of metrics. It also requires identifying which algorithmic ideas are central, which engineering details control practical performance, and which parts of the original system are simplified in a prototype. In this study, the largest gap between GuP and our implementation comes from the guarded candidate-space machinery and the efficiency of the nogood mechanism. This gap helps explain the difference between a sound algorithmic idea and a highly optimized system implementation.

Overall, the study shows the core behavior of GuP clearly. It shows that guard-based pruning, especially reservation-based pruning, can reduce the search space on real workloads, while also clarifying what would need to be improved in a more faithful future reproduction. The optional extension further suggests that workload-level reuse is a promising complementary direction: even without modifying the internal matcher, later queries in a refinement sequence can benefit from results that have already been computed.
